---
title: "UltimatumAnalysis"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

TO DO 
Define hypotheses / Describe variables
- Identify your model (outcome, likelihood function, predictors)
- Identify submodels for comparison
Define and motivate your priors 
- (predictive prior distribution?)
Assess model quality
- WAIC comparison
- Estimate comparison
- Predictive posterior
Report results
- Estimates and estimate interpretation
- Make sure to deal cautiously with interactions (e.g. plot!)
Compare current state of knowledge with previous
- E.g. prior vs. Posterior estimates



## Loading data, cleaning, and scaling relevant variables 
```{r cars}
library(pacman)
p_load(tidyverse, rethinking, pastecs, patchwork, Brobdingnag)

setwd("C:/Users/kilda/OneDrive/Documents/R")
library(pacman)
p_load(rethinking, pastecs, Brobdingnag)
library(tidyverse)


# loading data 
d1 = read.csv("U1.csv")
d2 = read.csv("U2.csv")
d3 = read.csv("U3.csv")
d4 = read.csv("U4.csv")
d5 = read.csv("U5.csv")
d6 = read.csv("U6.csv")
d7 = read.csv("U7.csv")
d8 = read.csv("U8.csv")
d9 = read.csv("U9.csv")
d10 = read.csv("U10.csv")
d11 = read.csv("U11.csv")
d12 = read.csv("U12.csv")
d13 = read.csv("U13.csv")

# combining
d = rbind(d1, d2, d3, d4, d5, d6, d7, d8, d9, d10, d11, d12, d13)

#cleaning irrelevant columns out 
df = data.frame(d$participant.id_in_session, d$participant.payoff, d$player.id_in_group, d$player.team, d$player.age, d$player.gender, d$player.group_id, d$player.payoff, d$group.amount_offered, d$group.offer_accepted, d$subsession.round_number, d$between_group_play, d$group_number)
df = df[complete.cases(df),] 
# gender : 
# df[df$d.player.gender %in% 'Female','d.player.gender'] <- 'null' 
df <- df[, -6] 

# data1 
data1 = data.frame(d$participant.id_in_session, d$participant.payoff, d$player.id_in_group, d$player.team, d$player.age, d$player.gender, d$player.group_id, d$player.payoff, d$group.amount_offered, d$group.offer_accepted, d$subsession.round_number, d$between_group_play, d$group_number)



```

## Running pipes for preliminary analysis & boxplots for comparison
# AMOUNT OFFERED 
```{r}
library(tidyverse)
library(dplyr)

# variables should be factors to function in ggplot
df$d.between_group_play = as.factor(df$d.between_group_play)
df$d.player.team = as.factor(df$d.player.team)

# trying to get pipes 
# looking at winning vs losing teams 
cond_sum = df %>%
  group_by(d.player.team) %>% 
   summarise(offered = mean(d.group.amount_offered))
cond_sum
# very similar regardless of winning or losing 
# boxplot


p1 <- ggplot(data=df, aes(x = d.player.team, y = d.group.amount_offered)) +
  geom_boxplot() +
  labs(title = "Effect of team on amount offered", x = "Winning team = 1, losing team = 2", y = "Amount offered")
p1


# looking at offers between and within groups 
group_type_sum = df %>%
  group_by(d.between_group_play == '1') %>% 
   summarise(offered = mean(d.group.amount_offered))
group_type_sum
# here we see a bit more of a difference 
# boxplot
p2 <- ggplot(data=df, aes(x = d.between_group_play, y = d.group.amount_offered)) +
  geom_boxplot() + 
  labs(title = "Effect of group on amount offered", x = "Between group", y = "Amount offered")
p2

# looking at group and team effect
comb_sum = df %>%
  group_by(d.between_group_play == '1', d.player.team == '1') %>% 
   summarise(offered = mean(d.group.amount_offered))
comb_sum
# boxplot 
p3 <- ggplot(data=df, aes(x = d.between_group_play=='1', y = d.group.amount_offered, colour = df$d.player.team=='1')) +
  geom_boxplot() +
  labs(title = "Effect of team and group on amount offered", x = "Between group", y = "Amount offered", colour = "winning team")
p3
# looks like there is a negative effect of within group and loosing

p3a <- ggplot(data=df, aes(x = d.player.team=='1', y = d.group.amount_offered, colour = df$d.between_group_play=='1')) +
   geom_boxplot() +
   labs(title = "Effect of team and group on amount offered", x = "Winning team", y = "Amount offered", colour = "between group")
p3a

####################################################################
## pipes looking at ACCEPTANCE RATE

# looking at overall acceptance rates 
sum(data1$d.group.offer_accepted == '1')
sum(data1$d.group.offer_accepted == '0')

# look at this as a function of the offer 

# winning or losing rate of acceptance 
team_cond_rate = data1 %>%
  group_by(d.player.team == '1') %>% 
   summarise(accept_rate = sum(d.group.offer_accepted == '1'))
team_cond_rate
# boxplot
df$d.between_group_play = as.factor(df$d.between_group_play)
df$d.player.team = as.factor(df$d.player.team)

p4 <- ggplot(df, aes(d.group.offer_accepted, ..count..)) +
  geom_bar(aes(fill = sum(d.group.offer_accepted == '1')), position = "dodge")
  
 # labs(title = "Effect of group on amount offered", x = "Between group", y = "Amount offered")
p4


# very similar regardless of winning or losing 
team_cond_rate1 = data1 %>%
  group_by(d.player.team == '1') %>% 
   summarise(accept_rate = sum(d.group.offer_accepted == '0'))
team_cond_rate1


# looking at offers between and within groups 
group_type_rate = data1 %>%
  group_by(d.between_group_play == '1') %>% 
   summarise(accept_rate =  sum(d.group.offer_accepted == '1'))
group_type_rate

group_type_rate1 = data1 %>%
  group_by(d.between_group_play == '1') %>% 
   summarise(accept_rate =  sum(d.group.offer_accepted == '0'))
group_type_rate1

# combining all 
comb_rate = data1 %>%
  group_by(d.between_group_play == '1', d.player.team == '1') %>% 
   summarise(accept_rate = sum(d.group.offer_accepted == '1'))
comb_rate

comb_rate1 = data1 %>%
  group_by(d.between_group_play == '1', d.player.team == '1') %>% 
   summarise(accept_rate = sum(d.group.offer_accepted == '0'))
comb_rate1
```



```{r}
## MODELZZZZZ 

# amount_offered ~ team_in_group 
# amount_offered ~ team_out_group 
# done by id_in_group = 1, and condition team = 1 (in), or 0 (out)

# amount_offered ~ condition + team 
# amount_offered ~ condition*team 

# acceptance_rate ~ condition 
# acceptance_rate ~ team 
# acceptance_rate ~ condition + team 
# acceptance_rate ~ condition*team 

# Step 1, add column to csv files 
# Step 2, Merge and load data files,
# Step 3,  Clean data files 
# Step 4 - check out the data (see results)
# step 5 - build bayesian models, see what we can predict 


# MONEY OFFERED MODELS 
# model for amount offered 
# model for effect of condition (player team) with radom effects of (participant ID (participant_id_in_session), experiment number (group number) & intercept)

######################################################################################################
# Scaling data for models
# combining
d = rbind(d1, d2, d3, d4, d5, d6, d7, d8, d9, d10, d11, d12, d13)

#cleaning irrelevant columns out 
df = data.frame(d$participant.id_in_session, d$participant.payoff, d$player.id_in_group, d$player.team, d$player.age, d$player.gender, d$player.group_id, d$player.payoff, d$group.amount_offered, d$group.offer_accepted, d$subsession.round_number, d$between_group_play, d$group_number)
df = df[complete.cases(df),] 
# gender : 
# df[df$d.player.gender %in% 'Female','d.player.gender'] <- 'null' 
df <- df[, -6] 

#df$d.group.amount_offered = df>[]
#df$d.player.gender

# we don't want to scale all columns 
df_1 = data.frame(df$d.participant.id_in_session, df$d.player.id_in_group, df$d.player.team,df$d.player.group_id, df$d.group.offer_accepted, df$d.subsession.round_number, df$d.between_group_play, df$d.group_number)  # add group_number
df <- df[, -c(1,3,4,6,9,10,11,12)] # add column number for variable group number 
# standardizing the data (centering and scaling)
df_s = scale(df, center = TRUE, scale = TRUE)
df_s = as.data.frame(df_s)
# new data frame
df = cbind(df_1, df_s)

#################################################################################################
```

## Models for amount offered 
```{r}
# model 1 - team condition 
df$df.d.player.team = as.character(df$df.d.player.team)
df$df.d.player.team[df$df.d.player.team == '1'] = '0'
df$df.d.player.team[df$df.d.player.team == '2'] = '1'
df$df.d.player.team = as.numeric(df$df.d.player.team)


m1 <- rethinking::map(
  alist(
    d.group.amount_offered ~ dnorm( mu , sigma ) , 
    mu <- ai + aii[df.d.participant.id_in_session] + aiii[df.d.group_number] + aB*df.d.player.team ,
    ai ~ dnorm(0, 1) , 
    aii[df.d.participant.id_in_session] ~ dnorm( 0 , 1 ) , 
    aiii[df.d.group_number] ~ dnorm(0, 1), 
    aB ~ dnorm( 1 , 0.2) , 
    sigma ~ dunif( 0 , 3 )
 ) ,  
 data = df)

precis(m1)
plot(precis(m1))

#use logistic in binomial 
# we can see that 


devtools::install_github("rmcelreath/rethinking", force = TRUE)
plot(precis(m1))

# model 2 - between group offering 
m2 <- rethinking::map(
  alist(
    d.group.amount_offered ~ dnorm( mu , sigma ) , 
    mu <- ai + aii[df.d.participant.id_in_session]+ aiii[df.d.group_number] + bB*df.d.between_group_play,
    ai ~ dnorm(0, 1) , 
    aii[df.d.participant.id_in_session] ~ dnorm( 0 , 1) , 
    aiii[df.d.group_number] ~ dnorm(0, 1), 
    bB ~ dnorm( 1 , 0.2) , 
    sigma ~ dunif( 0 , 3 )
 ) ,  
 data = df)

precis(m2)
devtools::install_github("rmcelreath/rethinking", force = TRUE)
plot(precis(m2))


# model 3 with both added together 
m3 <- rethinking::map(
  alist(
    d.group.amount_offered ~ dnorm( mu , sigma ) , 
    mu <- ai + aii[df.d.participant.id_in_session] + aiii[df.d.group_number] + bA*df.d.player.team + 
      bB*df.d.between_group_play,
    ai ~ dnorm(0, 1) , 
    aii[df.d.participant.id_in_session] ~ dnorm( 0 , 1 ) , 
    aiii[df.d.group_number] ~ dnorm(0, 1), 
    bA ~ dnorm( 1 , 0.2) , 
    bB ~ dnorm(1, 0.2) , 
    sigma ~ dunif( 0 , 3 )
 ) ,  
 data = df)

precis(m3, corr = TRUE)
devtools::install_github("rmcelreath/rethinking", force = TRUE)
plot(precis(m3))


# model with interaction of the two 
m4 <- rethinking::map(
  alist(
    d.group.amount_offered ~ dnorm( mu , sigma ) , 
    mu <- ai + aii[df.d.participant.id_in_session] + aiii[df.d.group_number] + bA*df.d.player.team + bB*df.d.between_group_play + bAB*df.d.player.team*df.d.between_group_play, 
    ai ~ dnorm(0, 1) , 
    aii[df.d.participant.id_in_session] ~ dnorm( 0 , 1) , 
    aiii[df.d.group_number] ~ dnorm(0, 1), 
    bA ~ dnorm( 1 , 0.2) , 
    bB ~ dnorm(1, 0.2) ,
    bAB ~ dnorm(1, 0.2), 
    sigma ~ dunif( 0 , 3 )
 ) ,  
 data = df)

precis(m4, corr = TRUE)
devtools::install_github("rmcelreath/rethinking", force = TRUE)
plot(precis(m4))
```

## WAIC comparisons of amount offered models 
```{r}
# making a WAIC comparison to choose the best model 
compare(m1, m2, m3, m4)

#beta difference 
coeftab(m1, m2, m3, m4)

# WAIC plot
devtools::install_github("rmcelreath/rethinking", force = TRUE)
plot(compare(m1, m2, m3, m4))


# coeftab plot 
plot(coeftab(m1, m2, m3, m4))

```


### MODELS GROUP OFFER ACCEPTED 
# for offer accepted, binomial distirbution with an interaction and look at rate of binomial distribution (is defined a linear model, same as in amount offered) + interaction 

```{r}
# m5, variable team conidtion 
#library(rethinking)
# making data for binomial model 
df_5 = data.frame(df$df.d.participant.id_in_session, df$df.d.group_number, df$df.d.group.offer_accepted, df$df.d.player.team)
library(plyr)
df_5 = rename(df_5, c("df.df.d.participant.id_in_session"="ID", "df.df.d.group_number"="GroupNumber", "df.df.d.group.offer_accepted"="AcceptanceRate", "df.df.d.player.team"="Team"))
#str(df_5)
df_5$ID = as.numeric(df_5$ID)
df_5$GroupNumber = as.numeric(df_5$GroupNumber)
df_5$AcceptanceRate = as.numeric(df_5$AcceptanceRate)
df_5$Team = as.numeric(df_5$Team)

df_5$Team= as.character(df_5$Team)
df_5$Team[df_5$Team == '1'] = '0'
df_5$Team[df_5$Team == '2'] = '1'
df_5$Team = as.numeric(df_5$Team)

#model 
m5 <- rethinking::map2stan( 
alist(
  AcceptanceRate ~ dbinom( 1 , p ) , 
  logit(p) <- ai + aii[ID] + aii[GroupNumber] + bA*Team,
  ai ~ dnorm(0,1),
  aii[ID] ~ dnorm(0,1),
  aiii[GroupNumber] ~ dnorm(0,1), 
  bA ~ dnorm(0, 0.2),
  sigma ~ dunif(0,3)
 ), 
data=df_5 , chains=2 , cores = 2, iter= 5000 , warmup=2000)

precis(m5)
plot(precis(m5))

# calculating relative probability 
logistic(-0.03)
logistic(c(0.29, 2.09))

logistic(1.22 -0.03)
logistic(1.22)
# almost no difference on the absolute scale for changing acceptance rate 

devtools::install_github("rmcelreath/rethinking", force = TRUE)
#pairs(m5)
plot(precis(m5))

# m6, variable between group play 
df_6 = data.frame(df$df.d.participant.id_in_session, df$df.d.group_number, df$df.d.group.offer_accepted, df$df.d.between_group_play)
library(plyr)
df_6 = rename(df_6, c("df.df.d.participant.id_in_session"="ID", "df.df.d.group_number"="GroupNumber", "df.df.d.group.offer_accepted"="AcceptanceRate", "df.df.d.between_group_play"="BetweenGroup"))
str(df_6) 
df_6$ID = as.numeric(df_6$ID)
df_6$GroupNumber = as.numeric(df_6$GroupNumber)
df_6$AcceptanceRate = as.numeric(df_6$AcceptanceRate)
df_6$BetweenGroup = as.numeric(df_6$BetweenGroup)


m6 <- map2stan( 
alist(
  AcceptanceRate ~ dbinom( 1 , p ) , 
  logit(p) <- ai + aii[ID] + aiii[GroupNumber] + bB*BetweenGroup,
  ai ~ dnorm(0,1),
  aii[ID] ~ dnorm(0,1),
  aiii[GroupNumber] ~ dnorm(0,1), 
  bB ~ dnorm(0, 0.2),
  sigma ~ dunif(0,3)
 ), 
data=df_6 , chains=2 , cores = 2, iter= 5000 , warmup=2000)

precis(m6)
devtools::install_github("rmcelreath/rethinking", force = TRUE)
plot(precis(m6))
plot(m6)

# calculating relative probability 
logistic(-0.07)
logistic(c(0.35, 2.10))

logistic(1.25 -0.07)
logistic(1.25)

# no difference on the absolute scale for changing acceptance rate 


# m7, model on between group play + team condition 
df_7 = data.frame(df$df.d.participant.id_in_session, df$df.d.group_number, df$df.d.group.offer_accepted, df$df.d.between_group_play, df$df.d.player.team)
#library(plyr)
df_7 = rename(df_7, c("df.df.d.participant.id_in_session"="ID", "df.df.d.group_number"="GroupNumber", "df.df.d.group.offer_accepted"="AcceptanceRate", "df.df.d.between_group_play"="BetweenGroup", "df.df.d.player.team"="Team"))
df_7$ID = as.numeric(df_7$ID)
df_7$GroupNumber = as.numeric(df_7$GroupNumber)
df_7$AcceptanceRate = as.numeric(df_7$AcceptanceRate)
df_7$BetweenGroup = as.numeric(df_7$BetweenGroup)
df_7$Team = as.numeric(df_7$Team)

df_7$Team= as.character(df_7$Team)
df_7$Team[df_7$Team == '1'] = '0'
df_7$Team[df_7$Team == '2'] = '1'
df_7$Team = as.numeric(df_7$Team)

m7 <- map2stan( 
alist(
  AcceptanceRate ~ dbinom( 1 , p ) , 
  logit(p) <- ai + aii[ID] + aiii[GroupNumber] + bB*BetweenGroup + bA*Team,
  ai ~ dnorm(0,1),
  aii[ID] ~ dnorm(0,1),
  aiii[GroupNumber] ~ dnorm(0,1), 
  bA ~ dnorm(0, 0.2),
  bB ~ dnorm(0, 0.2),
  sigma ~ dunif(0,3)
 ), 
data=df_7 , chains=2 , cores = 2, iter= 5000 , warmup=2000)

precis(m7, corr = TRUE)
# devtools::install_github("rmcelreath/rethinking", force = TRUE)
plot(precis(m7))

# calculating relative probability 
logistic(-0.03)
logistic(c(-0.32, 0.27))

logistic(1.25 -0.03)
logistic(1.25)

logistic(-0.07)
logistic(c(-0.38, 0.22))

logistic(1.25 -0.07)
logistic(1.25)
# no difference on the absolute scale for changing acceptance rate 

# m8, model on between group play*team condition 
df_8 = data.frame(df$df.d.participant.id_in_session, df$df.d.group_number, df$df.d.group.offer_accepted, df$df.d.between_group_play, df$df.d.player.team)
#library(plyr)
df_8 = rename(df_8, c("df.df.d.participant.id_in_session"="ID", "df.df.d.group_number"="GroupNumber", "df.df.d.group.offer_accepted"="AcceptanceRate", "df.df.d.between_group_play"="BetweenGroup", "df.df.d.player.team"="Team"))
df_8$ID = as.numeric(df_8$ID)
df_8$GroupNumber = as.numeric(df_8$GroupNumber)
df_8$AcceptanceRate = as.numeric(df_8$AcceptanceRate)
df_8$BetweenGroup = as.numeric(df_8$BetweenGroup)
df_8$Team = as.numeric(df_8$Team)

df_8$Team= as.character(df_8$Team)
df_8$Team[df_8$Team == '1'] = '0'
df_8$Team[df_8$Team == '2'] = '1'
df_8$Team = as.numeric(df_8$Team)


m8 <- map2stan( 
alist(
  AcceptanceRate ~ dbinom( 1 , p ) , 
  logit(p) <- ai + aii[ID] + aiii[GroupNumber] + bB*BetweenGroup + bA*Team + bR*Team*BetweenGroup,
  ai ~ dnorm(0,1),
  aii[ID] ~ dnorm(0,1),
  aiii[GroupNumber] ~ dnorm(0,1), 
  bA ~ dnorm(0, 0.2),
  bB ~ dnorm(0, 0.2),
  bR ~ dnorm(0, 0.2),
  sigma ~ dunif(0,3)
 ), 
data=df_8 , chains=2 , cores = 2, iter= 5000 , warmup=2000)

precis(m8)
precis(m8, depth = 2)
# devtools::install_github("rmcelreath/rethinking", force = TRUE)
plot(precis(m8))
# calculating relative probability 
logistic(-0.03)
logistic(c(-0.32, 0.28))

logistic(1.26 -0.03)
logistic(1.25)

logistic(-0.06)
logistic(c(-0.36, 0.24))

logistic(1.26 -0.07)
logistic(1.26)

logistic(-0.01)
logistic(c(-0.30, 0.30))

logistic(1.26 -0.01)
logistic(1.26)

# no difference on the absolute scale for changing acceptance rate 

```

## WAIC comparisons for Acceptance Rate models 
```{r}
# making a WAIC comparison to choose the best model 
compare(m5, m6, m7, m8)

#beta difference 
coeftab(m5, m6, m7, m8)

# WAIC plot
plot(compare(m5, m6, m7, m8))

# coeftab plot 
plot(coeftab(m5, m6, m7, m8))

```



## PLOTS FOR BEST AMOUNT OFFERED MODEL 
# Posterior predicitive plots 


```{r pressure, echo=FALSE}
############

#plotting likelihood

dens(rnorm( 10000, 0, 0.2))

# best of the models run predicted posterior and compare 



```

## Predicitve Posterior Plots for Best Amount offered model 
```{r}

m1 <- rethinking::map(
  alist(
    d.group.amount_offered ~ dnorm( mu , sigma ) , 
    mu <- ai + a[df.d.participant.id_in_session] + ab[df.d.group_number] + aB*df.d.player.team ,
    ai ~ dnorm(0, 1) , 
    a[df.d.participant.id_in_session] ~ dnorm( 0 , 1 ) , 
    ab[df.d.group_number] ~ dnorm(0, 1), 
    aB ~ dnorm( 1 , 0.2) , 
    sigma ~ dunif( 0 , 3 )
 ) ,  
 data = df)

precis(m1)
devtools::install_github("rmcelreath/rethinking", force = TRUE)
plot(precis(m1))

# Plot observations against predictions 
mu <- link(m1, na.rm = TRUE)
# summarize samples across cases
mu.mean <- apply( mu , 2 , mean )
mu.PI <- apply( mu , 2 , PI )
# simulate observations
# again no new data, so uses original data
model.sim <- sim( m1 , n=1000, na.rm = TRUE )
model.PI <- apply( model.sim , 2 , PI  )

# plot predictions against observed 
plot( mu.mean ~ df$d.group.amount_offered, col=rangi2 , ylim=range(mu.PI) ,
    xlab="Observed amount offered" , ylab="Predicted amount offered" )
abline( a=0 , b=1 , lty=2 )
for ( i in 1:nrow(df) )
    lines( rep(df$d.group.amount_offered[i],2) , c(mu.PI[1,i],mu.PI[2,i]) ,
        col=rangi2 )

########

#extracting samples from the posterior
post.samples=extract.samples(m1)

#plotting with the uncertainty
#just to check if the model makes sense
plot( d.group.amount_offered ~ df.d.player.team , df)
abline(a=coef(m1)['ai'], b=coef(m1)['aB'])
for ( i in 1:100 )
abline( a=post.samples$ai[i] , b=post.samples$aB[i] , col=col.alpha(rangi2, 0.5) )

###################################
# Can't make other plots with random effects in our model, so we have left them out 


####################################################




```


## PLOTS FOR ACCEPTANCE RATE MODELS 
```{r}
m6 <- map2stan( 
alist(
  AcceptanceRate ~ dbinom( 26 , p ) , 
  logit(p) <- ai + aii[ID] + aiii[GroupNumber] + bB*BetweenGroup,
  ai ~ dnorm(0,1),
  aii[ID] ~ dnorm(0,1),
  aiii[GroupNumber] ~ dnorm(0,1), 
  bB ~ dnorm(0, 0.2),
  sigma ~ dunif(0,3)
 ), 
data=df_6 , chains=2 , cores = 2, iter= 5000 , warmup=2000)

# extract Stan samples
post <- extract.samples(m6)
# Plot observations against predictions 
mu <- link(m6, na.rm = TRUE)
# summarize samples across cases
mu.mean <- apply( mu , 2 , mean )
mu.PI <- apply( mu , 2 , PI )
# simulate observations
# again no new data, so uses original data
model.sim <- sim( m6 , n=1000, na.rm = TRUE )
model.PI <- apply( model.sim , 2 , PI  )

# plot predictions against observed 
plot( mu.mean ~ df_6$AcceptanceRate, col=rangi2 , ylim=range(mu.PI) ,
    xlab="Observed acceptance rate" , ylab="Predicted acceptance rate" )
abline( a=0 , b=1 , lty=2 )
for ( i in 1:nrow(df_6) )
    lines( rep(df_6$AcceptanceRate[i],2) , c(mu.PI[1,i],mu.PI[2,i]) ,
        col=rangi2 )

#extracting samples from the posterior
post.samples=extract.samples(m6)

#plotting with the uncertainty
#just to check if the model makes sense
plot( AcceptanceRate ~ BetweenGroup, df_6)
abline(a=coef(m6)['ai'], b=coef(m6)['bB'])
for ( i in 1:nrow(df_6) )
abline( a=post.samples$ai[i] , b=post.samples$bB[i] , col=col.alpha(rangi2, 0.5) )




# will use by() here; see Overthinking box for explanation
link.m6 <- link( m6 , data=df_6 )
pred.p <- apply( link.m6 , 2 , mean )
pred.p.PI <- apply( link.m6 , 2 , PI )
plot( 0 , 0 , type="n" , xlab="between group" ,
ylab="acceptance rate " , ylim=c(0,10) , xaxt="n" ,
xlim=c(1,2) , yaxp=c(0,1,2) )
axis( 1 , at=1:4 , labels=c("0/0","1/0","0/1","1/1") )
mtext( paste( "participant" , df_6$ID ) )
p <- by( df_6$AcceptanceRate ,
list(df_6$BetweenGroup) , mean )
lines( 1:4  , col=rangi2 , lwd=2 )

######################################################################################
library(rethinking)
df_6 = as.data.frame(df_6)

post <- extract.samples( m6 ) 
post.samples = as.data.frame(post.samples)
p.acceptance_rate <- logistic( post$ai + post$bB )
quantile(c(0.025,0.5,0.975) )

for ( i in 1:4 ) {
x <- df_6$BetweenGroup
y1 <- df_6$AcceptanceRate[x]
y2 <- post$AcceptanceRate[x]
lines( x, y1, col=rangi2 , lwd=2 )
text( x+0.5 , (y1+y2)/2 + 0.05 , d$dept[x] , cex=0.8 , col=rangi2 )
}

qplot(p.acceptance_rate)

str(df_6)
df_6$ID = as.factor(df_6$ID)
df_6$AcceptanceRate = as.factor(df_6$AcceptanceRate)
df_6$BetweenGroup = as.factor(df_6$BetweenGroup)


ggplot(df_6, aes(ID, AcceptanceRate, colour = BetweenGroup)) + geom_boxplot()


```
Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
